---
title: "Structural Holes Results and Maps.Rmd"
author: "Bart Breekveldt"
date: "2022-11-01"
output: html_document
---

# Finding structural holes and create maps

## Loading libraries

```{r setup, include=FALSE}
packages = c('htmlwidgets','basemaps','dplyr','leaflet','sf','zoo','tidyr','knitr')

usePackage <- function(p) {
    if (!is.element(p, installed.packages()[,1]))
        install.packages(p, dep = TRUE)
    require(p, character.only = TRUE)
}

library(htmlwidgets)
library(basemaps)
library(dplyr)
library(leaflet)
library(sf)
library(zoo)
library(tidyr)
library(knitr)
```

## Load amenity/shop/transit facility type to all others betweenness edges information, bind df, summarise and store.

```{r counts}
# Load the files of betweenness count
path = "D:/EconNet/Paris/Betweenness Count/individual/"
files = list.files(path=path, pattern=NULL, all.files=FALSE,
           full.names=FALSE)

# bind all the dataframes together
df = data.frame()
for (i in files) {
  df = rbind(df, read.csv(paste0(path,'/',i)))
}

# summarise by osmids
cnt_osm = df %>%
  group_by(osmid_from, osmid_to) %>%
  summarise(n = sum(n))
cnt_osm = cnt_osm[order(cnt_osm$n, decreasing = TRUE), ]

# write the total file to csv
write.csv(cnt_osm,"D:/EconNet/Paris/Betweenness Count/total_kernel_edges.csv")

head(cnt_osm)
```

## Create one- and bi-directional keys, for bi-directional summarise both way betweenness edge count as one by the new key.
```{r keys}
# Determine min and max osm per edge, for determining betweenness count from both directions
from = unlist(as.list(cnt_osm[,'osmid_from']))
to = unlist(as.list(cnt_osm[,'osmid_to']))
min = c()
max = c()
onedir = c()
bidir = c()
for (i in 1:nrow(cnt_osm)) {
  min = append(min, min(from[i], to[i]))
  max = append(max, max(from[i], to[i]))
  onedir = append(onedir, paste0(from[i],'-',to[i]))
  bidir = append(bidir, paste0(min[i],'-',max[i]))
}
cnt_osm$min_osm = min
cnt_osm$max_osm = max
cnt_osm$key_onedir = onedir
cnt_osm$key_bidir = bidir


# Sum by the key of min-max osmid-edges
cnt2 = cnt_osm %>%
  group_by(key_bidir) %>%
  summarise(n = sum(n))
cnt2 = cnt2[order(cnt2$n, decreasing = TRUE), ]


head(cnt2)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

# Load the cleaned edges from before and create both one- and bidirectional keys from the edge direction, get distinct information.

```{r edges}
# Read the cleaned edge file
ce = read.csv("D:/EconNet/Paris/R_cleaned/edgesC_clean.csv")
ce = ce %>% select(-X)

# Add the counts to the edge-table
for (i in 1:nrow(ce)) {
  ce[i,'min_osm'] = min(ce[i,'u'], ce[i,'v'])
  ce[i,'max_osm'] = max(ce[i,'u'], ce[i,'v'])
  ce[i,'key_bidir'] = paste0(ce[i,'min_osm'],'-',ce[i,'max_osm'])
  ce[i,'key_onedir'] = paste0(ce[i,'u'],'-',ce[i,'v'])
}
# Read the geometry file
shp_ce_sf = read_sf("D:/EconNet/Paris/Cycling_City/BikeRoutes.shp")

# Add the counts to the edge-table
for (i in 1:nrow(shp_ce_sf)) {
  shp_ce_sf[i,'min_osm'] = min(shp_ce_sf$u[i], shp_ce_sf$v[i])
  shp_ce_sf[i,'max_osm'] = max(shp_ce_sf$u[i], shp_ce_sf$v[i])
  shp_ce_sf[i,'key_bidir'] = paste0(shp_ce_sf$min_osm[i],'-',
                                    shp_ce_sf$max_osm[i],'-')
  shp_ce_sf[i,'key_onedir'] = paste0(shp_ce_sf$u[i],'-',shp_ce_sf$v[i])
}

# Get distinct values, some node-osmids (from-to key) are double, remove them.
shp_ce_sf = shp_ce_sf %>% distinct(key_onedir, .keep_all = TRUE)

# Do this also for both the onedirectional and bidirectional. At the bidirectional one-side of the street gets also removed and the street is seen as one entity.
ce = ce %>% distinct(key_onedir, .keep_all = TRUE)
ce1 = ce %>% distinct(key_bidir, .keep_all = TRUE)

# Merge geometries with existing information
ce = merge(shp_ce_sf[c('key_onedir','geometry')], ce, by ='key_onedir')
ce1 = merge(shp_ce_sf[c('key_bidir','geometry')], ce1, by ='key_bidir')

# Write to shapefiles
st_write(ce, 'D:/EconNet/Paris/Check names road/ce.shp')
st_write(ce1, 'D:/EconNet/Paris/Check names road/ce1.shp')

head(ce)
```

## Merge on one- or bidirectional keys edge information, geometries and edge counts. Create an importance factor based on street penalties and form with edge betweenness the structural holes factor.

### First the bi-directional which we see as main, then the one-directional, which we seem as minor

```{r merging, echo=FALSE}
# Merge counts per bi-directional edge
ce1_merge = merge(ce1, cnt_osm, by = 'key_bidir')
ce1_merge = ce1_merge[,c('u','v','min_osm.x','max_osm.x','n','osmid','name','hwys','Ftype','clsp','Fsp','oneway','Fow','length','perc_length','lanes','Flane','geometry')]

# Determine importance factor by its penalties (importancy of road upgrade to design with less penalties)
ce1_merge['importance_factor'] = ((1+ce1_merge$Ftype) * (1+ce1_merge$Fsp) * (1+ce1_merge$Fow) * (1+ce1_merge$Flane))-1

# Betweenness counts (amount of road pieces on all routes between amenities/shops/transit facilities used)
ce1_merge['improve_importance_factor'] = (ce1_merge['importance_factor'])*ce1_merge$n
ce1_merge$n[is.na(ce1_merge$n)] <- 0

# Order to highlight largest values on top.
ce1_merge = ce1_merge[order(ce1_merge$n, decreasing = TRUE), ]
write.csv(ce1_merge, 'D:/EconNet/Paris/Betweenness Count/kernel_edges_bidrectional.csv')

# Merge per one-directional edge (and same formatting as the bi-directional ones)
ce2_merge = merge(ce, cnt_osm, by = 'key_onedir')
ce2_merge = ce2_merge[,c('u','v','min_osm.x','max_osm.x','n','osmid','name','hwys','Ftype','clsp','Fsp','oneway','Fow','length','perc_length','lanes','Flane','geometry')]
ce2_merge['importance_factor'] = ((1+ce2_merge$Ftype) * (1+ce2_merge$Fsp) * (1+ce2_merge$Fow) * (1+ce2_merge$Flane))-1
ce2_merge['improve_importance_factor'] = (ce2_merge['importance_factor'])*ce2_merge$n
ce2_merge$n[is.na(ce2_merge$n)] <- 0
ce2_merge = ce2_merge[order(ce2_merge$n, decreasing = TRUE), ]
write.csv(ce2_merge, 'D:/EconNet/Paris/Betweenness Count/kernel_edges_onedirectional.csv')
```
## Lets pre-process the cycleways for the graph and show a base map
``` {r bikegraph, echo = FALSE}
# Do the same thing with the bike lanes
st_bind_bike = st_bind[st_bind$hwys == 'cycleway',]

#st_bind_bike = st_bind[rownames(ce1[ce1$highway == 'cycleway',]),]
st_bind_bike = st_bind_bike[order(st_bind_bike$n),]

# The bike routes are set as green
palb <- colorFactor(palette = "Green",
                    domain = NULL)

# Extract the basemap of Paris in R.
base = basemap_magick(shp_ce_sf, map_service = "osm", map_type = "streets", p4s = 4326)

print(base)
```
## Focus on maps with bi-directional count, because cities often re-design the whole street, thus both ways of the cycle-network on that street. Results will be shown in graphs. First the edge betweenness count graph.

### The maps are interactive. You can zoom and click on streets for more information. The files are saved to an HTML widget with the saveWidget function.

``` {r GraphI, include = TRUE}
# Order to light on the focus area
st_bind = ce1_merge[order(ce1_merge$n),]

# Set a color palette. For the edge count this is a heatmap-like
pal <- colorNumeric(
  palette = c('#fff782','Orange','Red'),
  domain = st_bind$n)

# The bike routes are set as green
palb <- colorFactor(palette = "Green",
                    domain = NULL)

# Leaflets allow for smooth integration with sf.           
sf_lines = leaflet() %>%
  addTiles() %>%
  addPolylines(data = st_bind, color = ~pal(st_bind$n),
               # Log is used to balance the weight element
               weight = log(st_bind$n),
               # popups give information when a road is selected
               popup = paste0(st_bind$name,
                              "<br> <b> Type: </b>",st_bind$hwys,' (',st_bind$clsp,' km/h)',
                              "<br> <b> Times on route: </b>",st_bind$n,
                              "<br> <b> Road penalty: </b>",st_bind$importance_factor,
                              "<br> <b> Struc. hole score: </b>", round(st_bind$improve_importance_factor))) %>%
  addPolylines(data = st_bind_bike, color = 'green') %>%
  # Add legends to the graph
  addLegend(pal = pal, values = st_bind$n, position = "topright", title = 'Times on Route count') %>%
  addLegend(pal = palb, values = 'dedicated cycleway', position = "topright")

# print the graph
print(sf_lines)

# Save the graph as an interactive leaflet widget
saveWidget(sf_lines, file = "D:/EconNet/Paris/Leaflet maps/Betweenness_edges.html")

```

## Also for the second graph, which indicates the penalties resulting from its street design, and where the roads are situated in relation to the dedicated cycleways

``` {r GraphII, include = TRUE}
# Order to light on the focus area
st_bind = st_bind[order(st_bind$importance_factor),]

# Do the same for the importance factor
pal <- colorNumeric(
  palette = c('#b0d6e3','#ff41c3'),
  domain = st_bind$importance_factor)

sf_lines = leaflet() %>%
  addTiles() %>%
  addPolylines(data = st_bind, 
               color = ~pal(st_bind$importance_factor),
               weight = st_bind$importance_factor*20,
               popup = paste0(st_bind$name,
                              "<br> <b> Type: </b>",st_bind$hwys,' (',st_bind$clsp,' km/h)',
                              "<br> <b> Times on route: </b>",st_bind$n,
                              "<br> <b> Road penalty: </b>",st_bind$importance_factor,
                              "<br> <b> Struc. hole score: </b>", round(st_bind$improve_importance_factor))) %>%
  addPolylines(data = st_bind_bike, color = 'green') %>%
  addLegend(pal = pal, values = st_bind$importance_factor, position = "topright",title = 'Road penalty score') %>%
  addLegend(pal = palb, values = 'dedicated cycleway', position = "topright")

saveWidget(sf_lines, file = "D:/EconNet/Paris/Leaflet maps/Importance_factor.html")

sf_lines
```

## The third graph brings the edge betweenness count and the importance factor togheter in a improve importance factor, which roads need to be imroved first as a result of both these metrics. These we consider the structural holes of the network.

``` {r GraphIII, include = TRUE}
# Order to light on the focus area
st_bind = st_bind[order(st_bind$improve_importance_factor),]

# As for calculating the betweenness edges or structural holes
pal <- colorNumeric(
  palette = "Reds",
  domain = st_bind$improve_importance_factor)

sf_lines = leaflet() %>%
  addTiles() %>%
  addPolylines(data = st_bind, 
               color = ~pal(st_bind$improve_importance_factor),
               weight = log(st_bind$improve_importance_factor),
               popup = paste0(st_bind$name,
               "<br> <b> Type: </b>",st_bind$hwys,' (',st_bind$clsp,' km/h)',
               "<br> <b> Times on route: </b>",st_bind$n,
               "<br> <b> Road penalty: </b>",st_bind$importance_factor,
               "<br> <b> Struc. hole score: </b>", round(st_bind$improve_importance_factor))) %>%
  addPolylines(data = st_bind_bike, color = 'green') %>%
  addLegend(pal = pal, values = st_bind$improve_importance_factor, position = "topright",title = 'Structural hole score') %>%
  addLegend(pal = palb, values = 'dedicated cycleway', position = "topright")

print(sf_lines)

saveWidget(sf_lines, file = "D:/EconNet/Paris/Leaflet maps/Structural_holes.html")

```
